### 2012-09-22 sermons/Luke9:23-26.tex
Done.

>>>>

\I  Jeremiah 9:23-24, man's greatest glory
    \Q{ Thus says the LORD: "Let not the wise man glory in his wisdom, 
        let not the mighty man glory in his might, 
        nor let the rich man glory in his riches; 
        but let him who glories glory in this, 
        that he understands and knows Me, 
        That I am the LORD, exercising lovingkindness, judgment, 
        and righteousness in the earth. For in these I delight," says the LORD.}

\I  Ephesians 4:13, the goal of the Church
    \Q{ And He Himself gave some to be apostles, some prophets, 
        some evangelists, and some pastors and teachers, 
        for the equipping of the saints for the work of ministry, 
        for the edifying of the body of Christ, till we all come 
            to the unity of the faith 
        and of the knowledge of the Son of God, to a perfect man, 
        to the measure of the stature of the fullness of Christ; \ldots}
